Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-09-29 vesicle_code/docs/permeableVes/main.tex
adding new figures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in Stenosis}
We consider the effect of stenosis on a semi-permeable vesicle. To allow
for large amounts of fluid flux through the membrane, we consider
geometry with a long constricted region. We start by considering a
vesicle initialized with reduced area $\nu = 0.65$, and we compare the
vesicle shape when $\beta = 0$ (impermeable) and $\beta = 10^{-3}$
(permeable). Figure~\ref{fig:stenosisShape} shows the vesicles' shape at
several locations along the constriction. The colors along the left
channel represent the tension and those along the right represent the
flux. In Figure~\ref{fig:stenosisTensionAndFux}, the tension at location
$x=20$ and the flux at location $x=30$ are plotted with respect to
arclength. The value of $\theta=0$ corresponds to the nose of the
vesicle.
\begin{figure}[htp]
  \ifTikz
%  \scalebox{0.5}{\input{figures/stenosisShapeTension01.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux02.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeTension03.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeTension05.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeFlux06.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeTension07.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeTension09.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeFlux10.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension11.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
  \fi
  \caption{\label{fig:stenosisShape} An impermeable (dashed) and
  semi-permeable (solid) vesicle in a stenosed geometry (black).
  The vesicles' initial configuration are identical with reduced area
  $\nu = 0.65$. The color denotes the vesicles' tension (left) and flux
  (right). The semi-permeable vesicle deflates throughout the
  constriction (see Figure~\ref{fig:stenosisArea}) and develops higher
  curvature regions than its impermeable counterpart.}
\end{figure}

\begin{figure}[htp]
  \centering
  \ifTikz
  \scalebox{0.5}{\input{figures/stenosisTension09.tikz}}
  \scalebox{0.5}{\input{figures/stenosisFlux10.tikz}}
  \fi
  \caption{\label{fig:stenosisTensionAndFlux} The tension (left) and
  flux (right) of the semi-permeable (red) and impermeable (dashed blue)
  vesicles in Figure~\ref{fig:stenosisShape} at locations $x=20$ and
  $x=30$. The point $\theta=0$ corresponds to the right-most point of
  the vesicle.}
\end{figure}

@@

\begin{figure}[htp]
  \ifTikz
  \input{figures/stenosisBL.tikz}
  \fi
  \caption{\label{fig:stenosisBL} A stenosed semi-impermeable vesicle
  with reduced area 0.17. The initial reduced area is $0.20$. The bottom
  plot shows the velocity relative to the vesicle inside the square.
  The vesicle velocity in the square is nearly constant.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in Stenosis}
We consider the effect of stenosis on a semi-permeable vesicle. To allow
for large amounts of fluid flux through the membrane, we consider
geometry with a long constricted region. We start by considering a
vesicle initialized with reduced area $\nu = 0.65$, and we compare the
vesicle shape when $\beta = 0$ (impermeable) and $\beta = 10^{-3}$
(permeable). Figure~\ref{fig:stenosisShape} shows the vesicles' shape at
several locations along the constriction. The colors along the left
channel represent the tension and those along the right represent the
flux. In Figure~\ref{fig:stenosisTensionAndFlux}, the tension at
location $x=20$ and the flux at location $x=30$ are plotted with respect
to arclength. The value of $\theta=0$ corresponds to the nose of the
vesicle.
\begin{figure}[htp]
  \ifTikz
%  \scalebox{0.5}{\input{figures/stenosisShapeTension01.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux02.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension03.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension05.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux06.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension07.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension09.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux10.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension11.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeTension02.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeTension06.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeTension10.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
  \fi
  \caption{\label{fig:stenosisShape} An impermeable (dashed) and
  semi-permeable (solid) vesicle in a stenosed geometry (black).
  The vesicles' initial configuration are identical with reduced area
  $\nu = 0.65$. The color denotes the vesicles' tension (left) and flux
  (right). The semi-permeable vesicle deflates throughout the
  constriction (see Figure~\ref{fig:stenosisArea}) and develops higher
  curvature regions than its impermeable counterpart.}
\end{figure}

\begin{figure}[htp]
  \centering
  \ifTikz
  \scalebox{0.5}{\input{figures/stenosisTension12.tikz}}
  \scalebox{0.5}{\input{figures/stenosisFlux12.tikz}}
  \scalebox{0.5}{\input{figures/stenosisXvelocity12.tikz}}
  \scalebox{0.5}{\input{figures/stenosisYvelocity12.tikz}}
  \fi
  \caption{\label{fig:stenosisTensionAndFlux} The tension (top left), 
  flux (top right), $x$-velocity (bottom left), and $y$-velocity (bottom
  right) of the semi-permeable (red) and impermeable (dashed blue)
  vesicles in Figure~\ref{fig:stenosisShape} at location $x=50$. The
  point $\theta=0$ corresponds to the right-most point of the vesicle.}
\end{figure}

@@

\begin{figure}[htp]
%  \ifTikz
  \input{figures/stenosisBL.tikz}
%  \fi
  \caption{\label{fig:stenosisBL} A stenosed semi-impermeable (red) and
  imperemable (blue) vesicle. The semi-permeable vesicle has 
  reduced area 0.17, and both vesicles were initialized with reduce area
  $0.20$. The bottom plot shows the velocity relative to the vesicle
  inside the lubrication layer.  The vesicle velocity in the square is
  nearly constant (see Figure~\ref{fig:stenosisRA020Velocity}.}
\end{figure}

\begin{figure}[htp]
  \centering
  \ifTikz
  \scalebox{0.5}{\input{figures/stenosisXvelocityRA020.tikz}}
  \scalebox{0.5}{\input{figures/stenosisYvelocityRA020.tikz}}
  \fi
  \caption{\label{fig:stenosisRA020Velocity} The $x$ (left) and $y$
  (right) velocities of the vesicle in Figure~\ref{fig:stenosisBL}. The
  red lines correspond to the semi-permeable vesicle and the blue dashed
  lines correspond to the impermeable vesicle.}
\end{figure}
